Notes on area-length problem for CLE

### 2013-08-19 area-length/notes.tex
Bibliography added
Minor changes to area-length notes

\newtheorem{theorem}{Theorem}

@@

@@

@@

>>>>

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

@@

Though several publications exist
\cite{cardy2003exact,cardy2003crossover,cardy2001exact,cardy1994geometrical}
on this problem and the answer is
obtained from computer simulation \cite{richard2001scaling}, good understanding was not
obtained.

@@

Note that number of rooted loops of given area scales as the area to
the power minus one.

Define Hausdorff dimension as follows.
\begin{definition}
  {\it Hausdorff content} of the set $S$ is
  \begin{equation}
    \label{eq:3}
    C^d_H = \mathrm{inf} \sum_i r_i^d,
  \end{equation}
  where $\{r_i\}$ are such that there exists cover of $S$ by balls of
  radii $r_i>0$.

  {\it Hausdorff dimension}
  \begin{equation}
    \label{eq:4}
    d_H\equiv\mathrm{dim}_H(S) = \mathrm{inf}\{ d\geq 0: C^d_H(S)=0\}
  \end{equation}
\end{definition}

Consider loop of length $L$. The radius of the loop is connected with
the length as $L\sim R^{d_H}$. The area is related to radius $A\sim
R^2$, so $A\sim L^{\frac{2}{d_H}$.
(It is proved or almost proved in papers by Lawler).

For CLE the connection of Hausdorff dimension and parameter $\kappa$
is known:
\begin{equation}
  \label{eq:5}
  d_H=1+\frac{\kappa}{8}
\end{equation}

($\nu^{-1}=d_H$ ????)

At $x\to x_c$
\begin{equation}
  \label{eq:6}
  G^r(\mu,x)= \mu^{\theta} F\left(\frac{x-x_c}{\mu^{\phi}}\right)
\end{equation}

@@

\bibliography{bibliography}{} 
\bibliographystyle{utphys}
